Counterfactual Training

### 2024-12-18 paper/presenations/slides.qmd
uf

>>>>

## Planned Contributions

- Focus on enhancing trustworthiness and applicability of small opaque models. 
    - Add more datasets and neuro-tree models (relatively straightforward).
- Do not pitch as state-of-the-art approach to generative modelling similar to JEMs, but rather as an extension of JEMs to XAI and AR. 
- Limit use of image datasets to illustrate arguments:
    - Example: what happens if digit values can only be increased/decreased?
